---
title: "Data Pre-processing"

execute: 
  message: false
  warning: false
  eval: false
---

# Load Packages

```{r}
pacman::p_load(readxl, sf, tidyverse, tmap, sfdep, rvest, httr, jsonlite, onemapsgapi, ggpubr, olsrr,ggplot2, plotly)
```

# Import Datasets & Pre-process

## Resale Flat Prices (Aspatial)

Extract locations over study area 12 months, January 2022 to December 2022

```{r}
resale <- read_csv("data/aspatial/resale-flat-prices-based-on-registration-date-from-jan-2017-onwards.csv")

```

```{r}

#extract HDB study are of January 2022 to December 2022
resale<- resale %>% 
  filter(flat_type == "5 ROOM") %>%
  filter(month >= "2022-01" & month <= "2022-12")


resale$street_name <- gsub("ST\\.", "SAINT", resale$street_name)

#filter only unique HDB blocks
resale %>% distinct(street_name, block)
```

```{r}
geocode <- function(block, streetname) {
  base_url <- "https://developers.onemap.sg/commonapi/search"
  address <- paste(block, streetname, sep = " ")
  query <- list("searchVal" = address, 
                "returnGeom" = "Y",
                "getAddrDetails" = "N",
                "pageNum" = "1")
  
  res <- GET(base_url, query = query)
  restext<-content(res, as="text")
  
  output <- fromJSON(restext)  %>% 
    as.data.frame %>%
    select(results.LATITUDE, results.LONGITUDE)

  return(output)
}
```

```{r}
#| eval: false

resale$LATITUDE <- 0
resale$LONGITUDE <- 0

for (i in 1:nrow(resale)){
  temp_output <- geocode(resale[i, 4], resale[i, 5])
  
  resale$LATITUDE[i] <- temp_output$results.LATITUDE
  resale$LONGITUDE[i] <- temp_output$results.LONGITUDE
}
```

```{r}
#| eval: false

# resale flat with lat and long
write_rds(resale, "data/rds/resale_locations(1year).rds")
```

```{r}
resale_locations<-readRDS("data/rds/resale_locations(1year).rds")

#Transform
resale_sf <- st_as_sf(resale_locations, 
                      coords = c("LONGITUDE", 
                                 "LATITUDE"), 
                      crs=4326) %>%
  st_transform(crs = 3414)

#Missing values
sum(is.na(resale_sf))

#correct CRS
st_crs(resale_sf)


#invalid geometries
length(which(st_is_valid(resale_sf) == FALSE))


```

```{r}
#| eval: false
write_rds(resale_sf, "data/rds/resale_sf.rds")
```

# Geospatial

## Master Plan 2019 Boundary

```{r}
mpsz <- st_read(dsn="data/geospatial", layer="MPSZ-2019") %>%
  st_transform(crs=3414)
```

## Locational Factors Extracted via onemapAPI token

```{r}
#| eval: false
token <- get_token("email", "password")
```

```{r}
#| eval: false
avail_themes <-search_themes(token)
write_rds(avail_themes, "data/rds/available_themes.rds")
```

```{r}
#read the file for available themes
avail_themes<-readRDS("data/rds/available_themes.rds")

#sort by alphabetical order
avail_themes<-avail_themes[order(avail_themes$THEMENAME),]
avail_themes
```

```{r}
#| eval: false

#childcare
#retrieve the data such as the geometry and name  accordingly to the theme
childcare_tibble <- get_theme(token, "childcare")

# to convert a data frame of coordinates to an sf object and transform the crs information and create a shapefile for it
childcare_sf <- st_as_sf(childcare_tibble, coords=c("Lng", "Lat"),
                        crs=4326) %>% 
  st_transform(crs = 3414)

write_rds(childcare_sf, "data/rds/childcare_sf.rds")


#eldercare
eldercare_tibble <- get_theme(token, "eldercare")

eldercare_sf <- st_as_sf(eldercare_tibble, coords=c("Lng", "Lat"),
                         crs=4326) %>% 
  st_transform(crs = 3414)

write_rds(eldercare_sf, "data/rds/eldercare_sf.rds")


#kindergatens
kindergartens_tibble <- get_theme(token, "kindergartens")

kindergartens_sf <- st_as_sf(kindergartens_tibble, coords=c("Lng", "Lat"), 
                        crs=4326) %>% 
  st_transform(crs = 3414)
write_rds(kindergartens_sf, "data/rds/kindergartens_sf.rds")

#hawker Centres
hawkercentre_new_tibble <- get_theme(token, "hawkercentre_new")

hawkercentre_new_sf <- st_as_sf(hawkercentre_new_tibble, coords=c("Lng", "Lat"), 
                        crs=4326) %>% 
  st_transform(crs = 3414)

write_rds(hawkercentre_new_sf, "data/rds/hawkercentre_new_sf.rds")


#Healthier Hawker Centres, healthier_hawker_centres
hawkercentre_healthy_tibble <- get_theme(token, "healthier_hawker_centres")

hawkercentre_healthy_sf <- st_as_sf(hawkercentre_healthy_tibble, coords=c("Lng", "Lat"), 
                        crs=4326) %>% 
  st_transform(crs = 3414)

write_rds(hawkercentre_healthy_sf, "data/rds/hawkercentre_healthy_sf.rds")

#parks
nationalparks_tibble <- get_theme(token, "nationalparks")

nationalparks_sf <- st_as_sf(nationalparks_tibble, 
                             coords=c("Lng", "Lat"), crs=4326) %>%
  st_transform(crs = 3414)

write_rds(nationalparks_sf, "data/rds/nationalparks_sf.rds")

#Gyms@SG, exercisefacilities
gyms_tibble <- get_theme(token, "exercisefacilities")

gyms_sf <- st_as_sf(gyms_tibble, 
                             coords=c("Lng", "Lat"), crs=4326) %>%
  st_transform(crs = 3414)

write_rds(gyms_sf, "data/rds/gyms_sf.rds")

#Retail pharmacy locations , registered_pharmacy
pharmacy_tibble <- get_theme(token, "registered_pharmacy")

pharmacy_sf <- st_as_sf(pharmacy_tibble, 
                             coords=c("Lng", "Lat"), crs=4326) %>%
  st_transform(crs = 3414)

write_rds(pharmacy_sf, "data/rds/pharmacy_sf.rds")

#spf establishments, spf_establishments
spf_tibble <- get_theme(token, "spf_establishments")

spf_sf <- st_as_sf(spf_tibble, 
                             coords=c("Lng", "Lat"), crs=4326) %>%
  st_transform(crs = 3414)

write_rds(spf_sf, "data/rds/spf_sf.rds")


#HDB Car Park Information, 	hdb_car_park_information
HDB_carpark_tibble <- get_theme(token, "hdb_car_park_information")

HDB_carpark_sf <- st_as_sf(HDB_carpark_tibble, 
                             coords=c("Lng", "Lat"), crs=4326) %>%
  st_transform(crs = 3414)

write_rds(HDB_carpark_sf, "data/rds/HDB_carpark_sf.rds")

```

## Supermarket

```{r}
supermarket_sf <- st_read("data/geospatial/supermarkets-geojson.geojson") 
supermarket_sf <- supermarket_sf %>%
  st_transform(crs = 3414)
```

```{r}
#| eval: false
write_rds(supermarket_sf, "data/rds/supermarket_sf.rds")
```

## Bus Stop

```{r}
bus_stop<- st_read(dsn = "data/geospatial", layer = "BusStop")
bus_stop_sf <- bus_stop %>%
  st_transform(crs = 3414)
```

```{r}
#| eval: false
write_rds(bus_stop_sf, "data/rds/bus_stop_sf.rds")
```

## MRT/LRT

```{r}
mrt = st_read(dsn = "data/geospatial/", layer = "Train_Station_Exit_Layer")
mrt_sf <- mrt %>%
  st_transform(crs = 3414)
```

```{r}
#| eval: false
write_rds(mrt_sf, "data/rds/mrt_sf.rds")
```

## Primary School

```{r}
#| eval: false
primary_school <- read_csv("data/aspatial/general-information-of-schools.csv")

primary_school <- primary_school %>%
  filter(mainlevel_code == "PRIMARY") %>%
  select(school_name, address, postal_code)

primary_school<-primary_school %>%  
  filter(school_name!='JUYING PRIMARY SCHOOL')

```

```{r}
#| eval: false

primary_school$LATITUDE <- 0
primary_school$LONGITUDE <- 0

for (i in 1:nrow(primary_school)){
  temp_output <- geocode(primary_school[i, 1],"")

  primary_school$LATITUDE[i] <- temp_output$results.LATITUDE
  primary_school$LONGITUDE[i] <- temp_output$results.LONGITUDE
}
```

```{r}
#| eval: false
write_rds(primary_school, "data/rds/primary_school_locations.rds")
```

```{r}
primary_school_sf <- st_as_sf(primary_school,
                    coords = c("LONGITUDE", 
                               "LATITUDE"),
                    crs=4326) %>%
  st_transform(crs = 3414)
```

```{r}
#| eval: false
write_rds(primary_school_sf, "data/rds/primary_school_sf.rds")
```

## Top 10 Primary Schools

```{r}
#reference to:https://schoolbell.sg/primary-school-ranking/
popular_primary_schools <-c("Pei Hwa Presbyterian Primary School",
                            "Gongshang Primary School",
                            "Riverside Primary School",
                            "Red Swastika School",
                            "Punggol Green Primary School",
                            "Princess Elizabeth Primary School",
                            "Westwood Primary School",
                            "St. Hilda’s Primary School",
                            "Catholic High School (Primary Section)",
                            "Ai Tong School")

#make school names all uppercase
popular_primary_schools <- lapply(popular_primary_schools, toupper) 

# to check both primary school datasets matches
popular_primary_schools_sf <- primary_school_sf %>%
  filter(school_name %in% popular_primary_schools)

popular_primary_schools_sf <- popular_primary_schools_sf %>%
  rbind(primary_school_sf %>% filter(school_name == "CANOSSA CATHOLIC PRIMARY SCHOOL"))

popular_primary_schools_sf <- popular_primary_schools_sf %>%
  rbind(primary_school_sf %>% filter(school_name == "ST. HILDA'S PRIMARY SCHOOL"))

nrow(popular_primary_schools_sf)

```

```{r}
#| eval: false
write_rds(popular_primary_schools_sf, "data/rds/top10_primary_school_sf.rds")
```

## Shopping Mall

```{r}
shopping_mall <- read.csv("data/geospatial/mall_coordinates_updated.csv")

shopping_mall <- shopping_mall %>%
  select(name, latitude, longitude)

shopping_mall_sf <- st_as_sf(shopping_mall,
                        coords = c("longitude",
                                   "latitude"),
                        crs = 4326) %>%
  st_transform(crs = 3414)
```

```{r}
#| eval: false
write_rds(shopping_mall_sf, "data/rds/shopping_mall_sf.rds")
```

**Preprocess**

```{r}
#remove irrelevant columns

#childcare_sf
childcare_sf <- childcare_sf %>% select("NAME")

#eldercare_sf
eldercare_sf <- eldercare_sf %>% select("NAME")

#kindergartens_sf
kindergartens_sf <- kindergartens_sf %>% select("NAME")

#hawkercentre_new_sf
hawkercentre_new_sf <- hawkercentre_new_sf %>% select("NAME")

#hawkercentre_healthy_sf 
hawkercentre_healthy_sf  <- hawkercentre_healthy_sf  %>% select("NAME")

#nationalparks_sf
nationalparks_sf <- nationalparks_sf %>% select("NAME")

#gyms_sf
gyms_sf <- gyms_sf %>% select("NAME")
#pharmacy_sf
pharmacy_sf <- pharmacy_sf %>% select("NAME")
#spf_sf
spf_sf <- spf_sf %>% select("NAME")
#HDB_carpark_sf
HDB_carpark_sf <- HDB_carpark_sf %>% select("NAME","CAR_PARK_TYPE","TYPE_OF_PARKING_SYSTEM", "NIGHT_PARKING", "FREE_PARKING")

#supermarket
supermarket_sf$LIC_NAME <- str_extract(supermarket_sf$Description, "(?<=LIC_NAME<\\/th> <td>)[^<]+")
supermarket_sf <- supermarket_sf %>% select("LIC_NAME")

#bus stop
bus_stop_sf$stop_name <- paste(bus_stop_sf$BUS_STOP_N, bus_stop_sf$BUS_ROOF_N, bus_stop_sf$LOC_DESC)
bus_stop_sf <- bus_stop_sf %>% select("stop_name")

#mrt
#combine stn name and exit to make each row unique
mrt_sf$stn <- paste(mrt_sf$stn_name, mrt_sf$exit_code)
mrt_sf <- mrt_sf %>% select("stn")
```

```{r}
#missing values
sum(is.na(mpsz))
sum(is.na(childcare_sf))
sum(is.na(eldercare_sf))
sum(is.na(kindergartens_sf))
sum(is.na(hawkercentre_new_sf))
sum(is.na(hawkercentre_healthy_sf))
sum(is.na(nationalparks_sf))
sum(is.na(gyms_sf))
sum(is.na(pharmacy_sf))
sum(is.na(spf_sf))
sum(is.na(HDB_carpark_sf))
sum(is.na(supermarket_sf))
sum(is.na(bus_stop_sf))
sum(is.na(mrt_sf))
sum(is.na(primary_school_sf))
sum(is.na(popular_primary_schools_sf))
sum(is.na(shopping_mall_sf))

```

```{r}
length(which(st_is_valid(mpsz) == FALSE))
length(which(st_is_valid(childcare_sf) == FALSE))
length(which(st_is_valid(eldercare_sf) == FALSE))
length(which(st_is_valid(kindergartens_sf) == FALSE))
length(which(st_is_valid(hawkercentre_new_sf) == FALSE))
length(which(st_is_valid(hawkercentre_healthy_sf) == FALSE))
length(which(st_is_valid(nationalparks_sf) == FALSE))
length(which(st_is_valid(gyms_sf) == FALSE))
length(which(st_is_valid(pharmacy_sf) == FALSE))
length(which(st_is_valid(HDB_carpark_sf) == FALSE))
length(which(st_is_valid(supermarket_sf) == FALSE))
length(which(st_is_valid(bus_stop_sf) == FALSE))
length(which(st_is_valid(mrt_sf) == FALSE))
length(which(st_is_valid(primary_school_sf) == FALSE))
length(which(st_is_valid(popular_primary_schools_sf) == FALSE))
length(which(st_is_valid(shopping_mall_sf) == FALSE))

```

```{r}
mpsz <- st_make_valid(mpsz)
length(which(st_is_valid(mpsz) == FALSE))
```

## Rewrite sf.rds files with processed ver

```{r}
write_rds(mpsz, "data/rds/mpsz_sf.rds")
write_rds(childcare_sf, "data/rds/childcare_sf.rds")
write_rds(eldercare_sf, "data/rds/eldercare_sf.rds")
write_rds(kindergartens_sf, "data/rds/kindergartens_sf.rds")
write_rds(hawkercentre_new_sf, "data/rds/hawkercentre_new_sf.rds")
write_rds(hawkercentre_healthy_sf, "data/rds/hawkercentre_healthy_sf.rds")
write_rds(nationalparks_sf, "data/rds/nationalparks_sf.rds")
write_rds(gyms_sf, "data/rds/gyms_sf.rds")
write_rds(pharmacy_sf, "data/rds/pharmacy_sf.rds")
write_rds(spf_sf, "data/rds/spf_sf.rds")
write_rds(HDB_carpark_sf, "data/rds/HDB_carpark_sf.rds")
write_rds(supermarket_sf, "data/rds/supermarket_sf.rds")
write_rds(bus_stop_sf, "data/rds/bus_stop_sf.rds")
write_rds(mrt_sf, "data/rds/mrt_sf.rds")
write_rds(primary_school_sf, "data/rds/primary_school_sf.rds")
write_rds(popular_primary_schools_sf, "data/rds/top10_primary_school_sf.rds")
write_rds(shopping_mall_sf, "data/rds/shopping_mall_sf.rds")
```

# Import Processed Data

```{r}
resale_sf<-readRDS("data/rds/resale_sf.rds")

mpsz_sf<-readRDS("data/rds/mpsz_sf.rds")

childcare_sf <- readRDS("data/rds/childcare_sf.rds")
eldercare_sf<- readRDS("data/rds/eldercare_sf.rds")
kindergartens_sf <- readRDS("data/rds/kindergartens_sf.rds")
hawkercentre_new_sf <- readRDS("data/rds/hawkercentre_new_sf.rds")
hawkercentre_healthy_sf<-readRDS("data/rds/hawkercentre_healthy_sf.rds")
nationalparks_sf<-readRDS("data/rds/nationalparks_sf.rds")
gyms_sf <-readRDS("data/rds/gyms_sf.rds")
pharmacy_sf<-readRDS("data/rds/pharmacy_sf.rds")
spf_sf<-readRDS("data/rds/spf_sf.rds")
HDB_carpark_sf<-readRDS("data/rds/HDB_carpark_sf.rds")

supermarket_sf<-readRDS("data/rds/supermarket_sf.rds")
bus_stop_sf<-readRDS("data/rds/bus_stop_sf.rds")
mrt_sf<-readRDS("data/rds/mrt_sf.rds")
primary_school_sf<-readRDS("data/rds/primary_school_sf.rds")
top10_primary_school_sf<-readRDS("data/rds/top10_primary_school_sf.rds")
shopping_mall_sf<-readRDS("data/rds/shopping_mall_sf.rds")

```
