---
title: "Plotting Lixel"

execute: 
  message: false
  warning: false
  eval: false
---

For plotting lixel, will require:

-   HDB + Facility Points

-   Lixel

-   Shape

```{r}
pacman::p_load(sp, sf, rgdal, spNetwork, tmap, tidyverse)
```

```{r}
#| eval: false
area_names <- c("MARINE PARADE", "BUKIT MERAH", "QUEENSTOWN","OUTRAM", "ROCHOR", "KALLANG","TANGLIN", "CLEMENTI", "BEDOK", "JURONG EAST", "GEYLANG", "BUKIT TIMAH","NOVENA", "TOA PAYOH","TUAS", "JURONG WEST","SERANGOON", "BISHAN","TAMPINES", "BUKIT BATOK","HOUGANG", "ANG MO KIO","PASIR RIS", "BUKIT PANJANG", "YISHUN", "PUNGGOL","CHOA CHU KANG", "SENGKANG","SEMBAWANG", "WOODLANDS")
area_names <- gsub(" ", "_", area_names)
```

## Shape

```{r}
# set directory
setwd("data/rds/shape")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

# Childcare

::: panel-tabset
## Import Childcare RDS

```{r}
#| eval: false
# set directory
setwd("data/rds/facilities/combined/childcare")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Import Lixel

```{r}
#| eval: false
# set directory
setwd("data/rds/lixel/childcare")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Ang Mo Kio

```{r}
#| eval: false
tm_shape(shape_ANG_MO_KIO) +
  tm_polygons() +
tm_shape(lixel_childcare_ANG_MO_KIO)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_ANG_MO_KIO)+
  tm_dots(col = "Point Type")
```

## Bedok

```{r}
#| eval: false
tm_shape(shape_BEDOK) +
  tm_polygons() +
tm_shape(lixel_childcare_BEDOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_BEDOK)+
  tm_dots(col = "Point Type")
```

## Bishan

```{r}
#| eval: false
tm_shape(shape_BISHAN) +
  tm_polygons() +
tm_shape(lixel_childcare_BISHAN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_BISHAN)+
  tm_dots(col = "Point Type")
```

## Bukit Batok

```{r}
#| eval: false
tm_shape(shape_BUKIT_BATOK) +
  tm_polygons() +
tm_shape(lixel_childcare_BUKIT_BATOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_BUKIT_BATOK)+
  tm_dots(col = "Point Type")
```

## Bukit Merah

```{r}
#| eval: false
tm_shape(shape_BUKIT_MERAH) +
  tm_polygons() +
tm_shape(lixel_childcare_BUKIT_MERAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_BUKIT_MERAH)+
  tm_dots(col = "Point Type")
```

## Bukit Panjang

```{r}
#| eval: false
tm_shape(shape_BUKIT_PANJANG) +
  tm_polygons() +
tm_shape(lixel_childcare_BUKIT_PANJANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_BUKIT_PANJANG)+
  tm_dots(col = "Point Type")
```

## Bukit Timah

```{r}
#| eval: false
tm_shape(shape_BUKIT_TIMAH) +
  tm_polygons() +
tm_shape(lixel_childcare_BUKIT_TIMAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_BUKIT_TIMAH)+
  tm_dots(col = "Point Type")
```

## Choa Chu Kang

```{r}
#| eval: false
tm_shape(shape_CHOA_CHU_KANG) +
  tm_polygons() +
tm_shape(lixel_childcare_CHOA_CHU_KANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_CHOA_CHU_KANG)+
  tm_dots(col = "Point Type")
```

## Clementi

```{r}
#| eval: false
tm_shape(shape_CLEMENTI) +
  tm_polygons() +
tm_shape(lixel_childcare_CLEMENTI)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_CLEMENTI)+
  tm_dots(col = "Point Type")
```

## Geylang

```{r}
#| eval: false
tm_shape(shape_GEYLANG) +
  tm_polygons() +
tm_shape(lixel_childcare_GEYLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_GEYLANG)+
  tm_dots(col = "Point Type")
```

## Hougang

```{r}
#| eval: false
tm_shape(shape_HOUGANG) +
  tm_polygons() +
tm_shape(lixel_childcare_HOUGANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_HOUGANG)+
  tm_dots(col = "Point Type")
```

## Jurong East

```{r}
#| eval: false
tm_shape(shape_JURONG_EAST) +
  tm_polygons() +
tm_shape(lixel_childcare_JURONG_EAST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_JURONG_EAST)+
  tm_dots(col = "Point Type")
```

## Jurong West

```{r}
#| eval: false
tm_shape(shape_JURONG_WEST) +
  tm_polygons() +
tm_shape(lixel_childcare_JURONG_WEST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_JURONG_WEST)+
  tm_dots(col = "Point Type")
```

## Kallang

```{r}
#| eval: false
tm_shape(shape_KALLANG) +
  tm_polygons() +
tm_shape(lixel_childcare_KALLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_KALLANG)+
  tm_dots(col = "Point Type")
```

## Marine Parade

```{r}
#| eval: false
tm_shape(shape_MARINE_PARADE) +
  tm_polygons() +
tm_shape(lixel_childcare_MARINE_PARADE)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_MARINE_PARADE)+
  tm_dots(col = "Point Type")
```

## Novena

```{r}
#| eval: false
tm_shape(shape_NOVENA) +
  tm_polygons() +
tm_shape(lixel_childcare_NOVENA)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_NOVENA)+
  tm_dots(col = "Point Type")
```

## Outram

```{r}
#| eval: false
tm_shape(shape_OUTRAM) +
  tm_polygons() +
tm_shape(lixel_childcare_OUTRAM)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_OUTRAM)+
  tm_dots(col = "Point Type")
```

## Pasir Ris

```{r}
#| eval: false
tm_shape(shape_PASIR_RIS) +
  tm_polygons() +
tm_shape(lixel_childcare_PASIR_RIS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_PASIR_RIS)+
  tm_dots(col = "Point Type")
```

## Punggol

```{r}
#| eval: false
tm_shape(shape_PUNGGOL) +
  tm_polygons() +
tm_shape(lixel_childcare_PUNGGOL)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_PUNGGOL)+
  tm_dots(col = "Point Type")
```

## Queenstown

```{r}
#| eval: false
tm_shape(shape_QUEENSTOWN) +
  tm_polygons() +
tm_shape(lixel_childcare_QUEENSTOWN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_QUEENSTOWN)+
  tm_dots(col = "Point Type")
```

## Rochor

```{r}
#| eval: false
tm_shape(shape_ROCHOR) +
  tm_polygons() +
tm_shape(lixel_childcare_ROCHOR)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_ROCHOR)+
  tm_dots(col = "Point Type")
```

## Sembawang

```{r}
#| eval: false
tm_shape(shape_SEMBAWANG) +
  tm_polygons() +
tm_shape(lixel_childcare_SEMBAWANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_SEMBAWANG)+
  tm_dots(col = "Point Type")
```

## Sengkang

```{r}
#| eval: false
tm_shape(shape_SENGKANG) +
  tm_polygons() +
tm_shape(lixel_childcare_SENGKANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_SENGKANG)+
  tm_dots(col = "Point Type")
```

## Serangoon

```{r}
#| eval: false
tm_shape(shape_SERANGOON) +
  tm_polygons() +
tm_shape(lixel_childcare_SERANGOON)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_SERANGOON)+
  tm_dots(col = "Point Type")
```

## Tampines

```{r}
#| eval: false
tm_shape(shape_TAMPINES) +
  tm_polygons() +
tm_shape(lixel_childcare_TAMPINES)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_TAMPINES)+
  tm_dots(col = "Point Type")
```

## Tanglin

```{r}
#| eval: false
tm_shape(shape_TANGLIN) +
  tm_polygons() +
tm_shape(lixel_childcare_TANGLIN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_TANGLIN)+
  tm_dots(col = "Point Type")
```

## Toa Payoh

```{r}
#| eval: false
tm_shape(shape_TOA_PAYOH) +
  tm_polygons() +
tm_shape(lixel_childcare_TOA_PAYOH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_TOA_PAYOH)+
  tm_dots(col = "Point Type")
```

## Tuas

```{r}
#| eval: false
tm_shape(shape_TUAS) +
  tm_polygons() +
tm_shape(lixel_childcare_TUAS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_TUAS)+
  tm_dots(col = "Point Type")
```

## Woodlands

```{r}
#| eval: false
tm_shape(shape_WOODLANDS) +
  tm_polygons() +
tm_shape(lixel_childcare_WOODLANDS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_WOODLANDS)+
  tm_dots(col = "Point Type")
```

## Yishun

```{r}
#| eval: false
tm_shape(shape_YISHUN) +
  tm_polygons() +
tm_shape(lixel_childcare_YISHUN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_childcare_YISHUN)+
  tm_dots(col = "Point Type")
```

## Observation

-   3: punggol, sembawang

-   2.5: cck, bukit batok, yishun

-   2: sengkang

-   0: tuas
:::

# Eldercare

::: panel-tabset
## Import Eldercare RDS

```{r}
#| eval: false
# set directory
setwd("data/rds/facilities/combined/eldercare")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Import Lixel

```{r}
#| eval: false
# set directory
setwd("data/rds/lixel/eldercare")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Ang Mo Kio

```{r}
#| eval: false
tm_shape(shape_ANG_MO_KIO) +
  tm_polygons() +
tm_shape(lixel_eldercare_ANG_MO_KIO)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_ANG_MO_KIO)+
  tm_dots(col = "Point Type")
```

## Bedok

```{r}
#| eval: false
tm_shape(shape_BEDOK) +
  tm_polygons() +
tm_shape(lixel_eldercare_BEDOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_BEDOK)+
  tm_dots(col = "Point Type")
```

## Bishan

```{r}
#| eval: false
tm_shape(shape_BISHAN) +
  tm_polygons() +
tm_shape(lixel_eldercare_BISHAN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_BISHAN)+
  tm_dots(col = "Point Type")
```

## Bukit Batok

```{r}
#| eval: false
tm_shape(shape_BUKIT_BATOK) +
  tm_polygons() +
tm_shape(lixel_eldercare_BUKIT_BATOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_BUKIT_BATOK)+
  tm_dots(col = "Point Type")
```

## Bukit Merah

```{r}
#| eval: false
tm_shape(shape_BUKIT_MERAH) +
  tm_polygons() +
tm_shape(lixel_eldercare_BUKIT_MERAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_BUKIT_MERAH)+
  tm_dots(col = "Point Type")
```

## Bukit Panjang

```{r}
#| eval: false
tm_shape(shape_BUKIT_PANJANG) +
  tm_polygons() +
tm_shape(lixel_eldercare_BUKIT_PANJANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_BUKIT_PANJANG)+
  tm_dots(col = "Point Type")
```

## Bukit Timah

```{r}
#| eval: false
tm_shape(shape_BUKIT_TIMAH) +
  tm_polygons() +
tm_shape(lixel_eldercare_BUKIT_TIMAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_BUKIT_TIMAH)+
  tm_dots(col = "Point Type")
```

## Choa Chu Kang

```{r}
#| eval: false
tm_shape(shape_CHOA_CHU_KANG) +
  tm_polygons() +
tm_shape(lixel_eldercare_CHOA_CHU_KANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_CHOA_CHU_KANG)+
  tm_dots(col = "Point Type")
```

## Clementi

```{r}
#| eval: false
tm_shape(shape_CLEMENTI) +
  tm_polygons() +
tm_shape(lixel_eldercare_CLEMENTI)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_CLEMENTI)+
  tm_dots(col = "Point Type")
```

## Geylang

```{r}
#| eval: false
tm_shape(shape_GEYLANG) +
  tm_polygons() +
tm_shape(lixel_eldercare_GEYLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_GEYLANG)+
  tm_dots(col = "Point Type")
```

## Hougang

```{r}
#| eval: false
tm_shape(shape_HOUGANG) +
  tm_polygons() +
tm_shape(lixel_eldercare_HOUGANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_HOUGANG)+
  tm_dots(col = "Point Type")
```

## Jurong East

```{r}
#| eval: false
tm_shape(shape_JURONG_EAST) +
  tm_polygons() +
tm_shape(lixel_eldercare_JURONG_EAST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_JURONG_EAST)+
  tm_dots(col = "Point Type")
```

## Jurong West

```{r}
#| eval: false
tm_shape(shape_JURONG_WEST) +
  tm_polygons() +
tm_shape(lixel_eldercare_JURONG_WEST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_JURONG_WEST)+
  tm_dots(col = "Point Type")
```

## Kallang

```{r}
#| eval: false
tm_shape(shape_KALLANG) +
  tm_polygons() +
tm_shape(lixel_eldercare_KALLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_KALLANG)+
  tm_dots(col = "Point Type")
```

## Marine Parade

```{r}
#| eval: false
tm_shape(shape_MARINE_PARADE) +
  tm_polygons() +
tm_shape(lixel_eldercare_MARINE_PARADE)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_MARINE_PARADE)+
  tm_dots(col = "Point Type")
```

## Novena

```{r}
#| eval: false
tm_shape(shape_NOVENA) +
  tm_polygons() +
tm_shape(lixel_eldercare_NOVENA)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_NOVENA)+
  tm_dots(col = "Point Type")
```

## Outram

```{r}
#| eval: false
tm_shape(shape_OUTRAM) +
  tm_polygons() +
tm_shape(lixel_eldercare_OUTRAM)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_OUTRAM)+
  tm_dots(col = "Point Type")
```

## Pasir Ris

```{r}
#| eval: false
tm_shape(shape_PASIR_RIS) +
  tm_polygons() +
tm_shape(lixel_eldercare_PASIR_RIS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_PASIR_RIS)+
  tm_dots(col = "Point Type")
```

## Punggol

```{r}
#| eval: false
tm_shape(shape_PUNGGOL) +
  tm_polygons() +
tm_shape(lixel_eldercare_PUNGGOL)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_PUNGGOL)+
  tm_dots(col = "Point Type")
```

## Queenstown

```{r}
#| eval: false
tm_shape(shape_QUEENSTOWN) +
  tm_polygons() +
tm_shape(lixel_eldercare_QUEENSTOWN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_QUEENSTOWN)+
  tm_dots(col = "Point Type")
```

## Rochor

```{r}
#| eval: false
tm_shape(shape_ROCHOR) +
  tm_polygons() +
tm_shape(lixel_eldercare_ROCHOR)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_ROCHOR)+
  tm_dots(col = "Point Type")
```

## Sembawang

```{r}
#| eval: false
tm_shape(shape_SEMBAWANG) +
  tm_polygons() +
tm_shape(lixel_eldercare_SEMBAWANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_SEMBAWANG)+
  tm_dots(col = "Point Type")
```

## Sengkang

```{r}
#| eval: false
tm_shape(shape_SENGKANG) +
  tm_polygons() +
tm_shape(lixel_eldercare_SENGKANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_SENGKANG)+
  tm_dots(col = "Point Type")
```

## Serangoon

```{r}
#| eval: false
tm_shape(shape_SERANGOON) +
  tm_polygons() +
tm_shape(lixel_eldercare_SERANGOON)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_SERANGOON)+
  tm_dots(col = "Point Type")
```

## Tampines

```{r}
#| eval: false
tm_shape(shape_TAMPINES) +
  tm_polygons() +
tm_shape(lixel_eldercare_TAMPINES)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_TAMPINES)+
  tm_dots(col = "Point Type")
```

## Tanglin

```{r}
#| eval: false
tm_shape(shape_TANGLIN) +
  tm_polygons() +
tm_shape(lixel_eldercare_TANGLIN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_TANGLIN)+
  tm_dots(col = "Point Type")
```

## Toa Payoh

```{r}
#| eval: false
tm_shape(shape_TOA_PAYOH) +
  tm_polygons() +
tm_shape(lixel_eldercare_TOA_PAYOH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_TOA_PAYOH)+
  tm_dots(col = "Point Type")
```

## Tuas

```{r}
#| eval: false
tm_shape(shape_TUAS) +
  tm_polygons() +
tm_shape(lixel_eldercare_TUAS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_TUAS)+
  tm_dots(col = "Point Type")
```

## Woodlands

```{r}
#| eval: false
tm_shape(shape_WOODLANDS) +
  tm_polygons() +
tm_shape(lixel_eldercare_WOODLANDS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_WOODLANDS)+
  tm_dots(col = "Point Type")
```

## Yishun

```{r}
#| eval: false
tm_shape(shape_YISHUN) +
  tm_polygons() +
tm_shape(lixel_eldercare_YISHUN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_eldercare_YISHUN)+
  tm_dots(col = "Point Type")
```

## Observation

-   3: punggol, sembawang

-   2.5: bukit batok, cck, yishun

-   0: tuas
:::

# Kindergarten

::: panel-tabset
## Import Kindergarten RDS

```{r}
#| eval: false
# set directory
setwd("data/rds/facilities/combined/kindergarten")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Import Lixel

```{r}
#| eval: false
# set directory
setwd("data/rds/lixel/kindergarten")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Ang Mo Kio

```{r}
#| eval: false
tm_shape(shape_ANG_MO_KIO) +
  tm_polygons() +
tm_shape(lixel_kindergarten_ANG_MO_KIO)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_ANG_MO_KIO)+
  tm_dots(col = "Point Type")
```

## Bedok

```{r}
#| eval: false
tm_shape(shape_BEDOK) +
  tm_polygons() +
tm_shape(lixel_kindergarten_BEDOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_BEDOK)+
  tm_dots(col = "Point Type")
```

## Bishan

```{r}
#| eval: false
tm_shape(shape_BISHAN) +
  tm_polygons() +
tm_shape(lixel_kindergarten_BISHAN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_BISHAN)+
  tm_dots(col = "Point Type")
```

## Bukit Batok

```{r}
#| eval: false
tm_shape(shape_BUKIT_BATOK) +
  tm_polygons() +
tm_shape(lixel_kindergarten_BUKIT_BATOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_BUKIT_BATOK)+
  tm_dots(col = "Point Type")
```

## Bukit Merah

```{r}
#| eval: false
tm_shape(shape_BUKIT_MERAH) +
  tm_polygons() +
tm_shape(lixel_kindergarten_BUKIT_MERAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_BUKIT_MERAH)+
  tm_dots(col = "Point Type")
```

## Bukit Panjang

```{r}
#| eval: false
tm_shape(shape_BUKIT_PANJANG) +
  tm_polygons() +
tm_shape(lixel_kindergarten_BUKIT_PANJANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_BUKIT_PANJANG)+
  tm_dots(col = "Point Type")
```

## Bukit Timah

```{r}
#| eval: false
tm_shape(shape_BUKIT_TIMAH) +
  tm_polygons() +
tm_shape(lixel_kindergarten_BUKIT_TIMAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_BUKIT_TIMAH)+
  tm_dots(col = "Point Type")
```

## Choa Chu Kang

```{r}
#| eval: false
tm_shape(shape_CHOA_CHU_KANG) +
  tm_polygons() +
tm_shape(lixel_kindergarten_CHOA_CHU_KANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_CHOA_CHU_KANG)+
  tm_dots(col = "Point Type")
```

## Clementi

```{r}
#| eval: false
tm_shape(shape_CLEMENTI) +
  tm_polygons() +
tm_shape(lixel_kindergarten_CLEMENTI)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_CLEMENTI)+
  tm_dots(col = "Point Type")
```

## Geylang

```{r}
#| eval: false
tm_shape(shape_GEYLANG) +
  tm_polygons() +
tm_shape(lixel_kindergarten_GEYLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_GEYLANG)+
  tm_dots(col = "Point Type")
```

## Hougang

```{r}
#| eval: false
tm_shape(shape_HOUGANG) +
  tm_polygons() +
tm_shape(lixel_kindergarten_HOUGANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_HOUGANG)+
  tm_dots(col = "Point Type")
```

## Jurong East

```{r}
#| eval: false
tm_shape(shape_JURONG_EAST) +
  tm_polygons() +
tm_shape(lixel_kindergarten_JURONG_EAST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_JURONG_EAST)+
  tm_dots(col = "Point Type")
```

## Jurong West

```{r}
#| eval: false
tm_shape(shape_JURONG_WEST) +
  tm_polygons() +
tm_shape(lixel_kindergarten_JURONG_WEST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_JURONG_WEST)+
  tm_dots(col = "Point Type")
```

## Kallang

```{r}
#| eval: false
tm_shape(shape_KALLANG) +
  tm_polygons() +
tm_shape(lixel_kindergarten_KALLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_KALLANG)+
  tm_dots(col = "Point Type")
```

## Marine Parade

```{r}
#| eval: false
tm_shape(shape_MARINE_PARADE) +
  tm_polygons() +
tm_shape(lixel_kindergarten_MARINE_PARADE)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_MARINE_PARADE)+
  tm_dots(col = "Point Type")
```

## Novena

```{r}
#| eval: false
tm_shape(shape_NOVENA) +
  tm_polygons() +
tm_shape(lixel_kindergarten_NOVENA)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_NOVENA)+
  tm_dots(col = "Point Type")
```

## Outram

```{r}
#| eval: false
tm_shape(shape_OUTRAM) +
  tm_polygons() +
tm_shape(lixel_kindergarten_OUTRAM)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_OUTRAM)+
  tm_dots(col = "Point Type")
```

## Pasir Ris

```{r}
#| eval: false
tm_shape(shape_PASIR_RIS) +
  tm_polygons() +
tm_shape(lixel_kindergarten_PASIR_RIS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_PASIR_RIS)+
  tm_dots(col = "Point Type")
```

## Punggol

```{r}
#| eval: false
tm_shape(shape_PUNGGOL) +
  tm_polygons() +
tm_shape(lixel_kindergarten_PUNGGOL)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_PUNGGOL)+
  tm_dots(col = "Point Type")
```

## Queenstown

```{r}
#| eval: false
tm_shape(shape_QUEENSTOWN) +
  tm_polygons() +
tm_shape(lixel_kindergarten_QUEENSTOWN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_QUEENSTOWN)+
  tm_dots(col = "Point Type")
```

## Rochor

```{r}
#| eval: false
tm_shape(shape_ROCHOR) +
  tm_polygons() +
tm_shape(lixel_kindergarten_ROCHOR)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_ROCHOR)+
  tm_dots(col = "Point Type")
```

## Sembawang

```{r}
#| eval: false
tm_shape(shape_SEMBAWANG) +
  tm_polygons() +
tm_shape(lixel_kindergarten_SEMBAWANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_SEMBAWANG)+
  tm_dots(col = "Point Type")
```

## Sengkang

```{r}
#| eval: false
tm_shape(shape_SENGKANG) +
  tm_polygons() +
tm_shape(lixel_kindergarten_SENGKANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_SENGKANG)+
  tm_dots(col = "Point Type")
```

## Serangoon

```{r}
#| eval: false
tm_shape(shape_SERANGOON) +
  tm_polygons() +
tm_shape(lixel_kindergarten_SERANGOON)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_SERANGOON)+
  tm_dots(col = "Point Type")
```

## Tampines

```{r}
#| eval: false
tm_shape(shape_TAMPINES) +
  tm_polygons() +
tm_shape(lixel_kindergarten_TAMPINES)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_TAMPINES)+
  tm_dots(col = "Point Type")
```

## Tanglin

```{r}
#| eval: false
tm_shape(shape_TANGLIN) +
  tm_polygons() +
tm_shape(lixel_kindergarten_TANGLIN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_TANGLIN)+
  tm_dots(col = "Point Type")
```

## Toa Payoh

```{r}
#| eval: false
tm_shape(shape_TOA_PAYOH) +
  tm_polygons() +
tm_shape(lixel_kindergarten_TOA_PAYOH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_TOA_PAYOH)+
  tm_dots(col = "Point Type")
```

## Tuas

```{r}
#| eval: false
tm_shape(shape_TUAS) +
  tm_polygons() +
tm_shape(lixel_kindergarten_TUAS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_TUAS)+
  tm_dots(col = "Point Type")
```

## Woodlands

```{r}
#| eval: false
tm_shape(shape_WOODLANDS) +
  tm_polygons() +
tm_shape(lixel_kindergarten_WOODLANDS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_WOODLANDS)+
  tm_dots(col = "Point Type")
```

## Yishun

```{r}
#| eval: false
tm_shape(shape_YISHUN) +
  tm_polygons() +
tm_shape(lixel_kindergarten_YISHUN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_kindergarten_YISHUN)+
  tm_dots(col = "Point Type")
```

## Observation
:::

# New Hawkers

::: panel-tabset
## Import New Hawkers RDS

```{r}
#| eval: false
# set directory
setwd("data/rds/facilities/combined/hawker_new")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Import Lixel

```{r}
#| eval: false
# set directory
setwd("data/rds/lixel/hawker_new")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Ang Mo Kio

```{r}
#| eval: false
tm_shape(shape_ANG_MO_KIO) +
  tm_polygons() +
tm_shape(lixel_hawker_new_ANG_MO_KIO)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_ANG_MO_KIO)+
  tm_dots(col = "Point Type")
```

## Bedok

```{r}
#| eval: false
tm_shape(shape_BEDOK) +
  tm_polygons() +
tm_shape(lixel_hawker_new_BEDOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_BEDOK)+
  tm_dots(col = "Point Type")
```

## Bishan

```{r}
#| eval: false
tm_shape(shape_BISHAN) +
  tm_polygons() +
tm_shape(lixel_hawker_new_BISHAN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_BISHAN)+
  tm_dots(col = "Point Type")
```

## Bukit Batok

```{r}
#| eval: false
tm_shape(shape_BUKIT_BATOK) +
  tm_polygons() +
tm_shape(lixel_hawker_new_BUKIT_BATOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_BUKIT_BATOK)+
  tm_dots(col = "Point Type")
```

## Bukit Merah

```{r}
#| eval: false
tm_shape(shape_BUKIT_MERAH) +
  tm_polygons() +
tm_shape(lixel_hawker_new_BUKIT_MERAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_BUKIT_MERAH)+
  tm_dots(col = "Point Type")
```

## Bukit Panjang

```{r}
#| eval: false
tm_shape(shape_BUKIT_PANJANG) +
  tm_polygons() +
tm_shape(lixel_hawker_new_BUKIT_PANJANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_BUKIT_PANJANG)+
  tm_dots(col = "Point Type")
```

## Bukit Timah

```{r}
#| eval: false
tm_shape(shape_BUKIT_TIMAH) +
  tm_polygons() +
tm_shape(lixel_hawker_new_BUKIT_TIMAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_BUKIT_TIMAH)+
  tm_dots(col = "Point Type")
```

## Choa Chu Kang

```{r}
#| eval: false
tm_shape(shape_CHOA_CHU_KANG) +
  tm_polygons() +
tm_shape(lixel_hawker_new_CHOA_CHU_KANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_CHOA_CHU_KANG)+
  tm_dots(col = "Point Type")
```

## Clementi

```{r}
#| eval: false
tm_shape(shape_CLEMENTI) +
  tm_polygons() +
tm_shape(lixel_hawker_new_CLEMENTI)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_CLEMENTI)+
  tm_dots(col = "Point Type")
```

## Geylang

```{r}
#| eval: false
tm_shape(shape_GEYLANG) +
  tm_polygons() +
tm_shape(lixel_hawker_new_GEYLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_GEYLANG)+
  tm_dots(col = "Point Type")
```

## Hougang

```{r}
#| eval: false
tm_shape(shape_HOUGANG) +
  tm_polygons() +
tm_shape(lixel_hawker_new_HOUGANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_HOUGANG)+
  tm_dots(col = "Point Type")
```

## Jurong East

```{r}
#| eval: false
tm_shape(shape_JURONG_EAST) +
  tm_polygons() +
tm_shape(lixel_hawker_new_JURONG_EAST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_JURONG_EAST)+
  tm_dots(col = "Point Type")
```

## Jurong West

```{r}
#| eval: false
tm_shape(shape_JURONG_WEST) +
  tm_polygons() +
tm_shape(lixel_hawker_new_JURONG_WEST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_JURONG_WEST)+
  tm_dots(col = "Point Type")
```

## Kallang

```{r}
#| eval: false
tm_shape(shape_KALLANG) +
  tm_polygons() +
tm_shape(lixel_hawker_new_KALLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_KALLANG)+
  tm_dots(col = "Point Type")
```

## Marine Parade

```{r}
#| eval: false
tm_shape(shape_MARINE_PARADE) +
  tm_polygons() +
tm_shape(lixel_hawker_new_MARINE_PARADE)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_MARINE_PARADE)+
  tm_dots(col = "Point Type")
```

## Novena

```{r}
#| eval: false
tm_shape(shape_NOVENA) +
  tm_polygons() +
tm_shape(lixel_hawker_new_NOVENA)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_NOVENA)+
  tm_dots(col = "Point Type")
```

## Outram

```{r}
#| eval: false
tm_shape(shape_OUTRAM) +
  tm_polygons() +
tm_shape(lixel_hawker_new_OUTRAM)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_OUTRAM)+
  tm_dots(col = "Point Type")
```

## Pasir Ris

```{r}
#| eval: false
tm_shape(shape_PASIR_RIS) +
  tm_polygons() +
tm_shape(lixel_hawker_new_PASIR_RIS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_PASIR_RIS)+
  tm_dots(col = "Point Type")
```

## Punggol

```{r}
#| eval: false
tm_shape(shape_PUNGGOL) +
  tm_polygons() +
tm_shape(lixel_hawker_new_PUNGGOL)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_PUNGGOL)+
  tm_dots(col = "Point Type")
```

## Queenstown

```{r}
#| eval: false
tm_shape(shape_QUEENSTOWN) +
  tm_polygons() +
tm_shape(lixel_hawker_new_QUEENSTOWN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_QUEENSTOWN)+
  tm_dots(col = "Point Type")
```

## Rochor

```{r}
#| eval: false
tm_shape(shape_ROCHOR) +
  tm_polygons() +
tm_shape(lixel_hawker_new_ROCHOR)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_ROCHOR)+
  tm_dots(col = "Point Type")
```

## Sembawang

```{r}
#| eval: false
tm_shape(shape_SEMBAWANG) +
  tm_polygons() +
tm_shape(lixel_hawker_new_SEMBAWANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_SEMBAWANG)+
  tm_dots(col = "Point Type")
```

## Sengkang

```{r}
#| eval: false
tm_shape(shape_SENGKANG) +
  tm_polygons() +
tm_shape(lixel_hawker_new_SENGKANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_SENGKANG)+
  tm_dots(col = "Point Type")
```

## Serangoon

```{r}
#| eval: false
tm_shape(shape_SERANGOON) +
  tm_polygons() +
tm_shape(lixel_hawker_new_SERANGOON)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_SERANGOON)+
  tm_dots(col = "Point Type")
```

## Tampines

```{r}
#| eval: false
tm_shape(shape_TAMPINES) +
  tm_polygons() +
tm_shape(lixel_hawker_new_TAMPINES)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_TAMPINES)+
  tm_dots(col = "Point Type")
```

## Tanglin

```{r}
#| eval: false
tm_shape(shape_TANGLIN) +
  tm_polygons() +
tm_shape(lixel_hawker_new_TANGLIN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_TANGLIN)+
  tm_dots(col = "Point Type")
```

## Toa Payoh

```{r}
#| eval: false
tm_shape(shape_TOA_PAYOH) +
  tm_polygons() +
tm_shape(lixel_hawker_new_TOA_PAYOH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_TOA_PAYOH)+
  tm_dots(col = "Point Type")
```

## Tuas

```{r}
#| eval: false
tm_shape(shape_TUAS) +
  tm_polygons() +
tm_shape(lixel_hawker_new_TUAS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_TUAS)+
  tm_dots(col = "Point Type")
```

## Woodlands

```{r}
#| eval: false
tm_shape(shape_WOODLANDS) +
  tm_polygons() +
tm_shape(lixel_hawker_new_WOODLANDS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_WOODLANDS)+
  tm_dots(col = "Point Type")
```

## Yishun

```{r}
#| eval: false
tm_shape(shape_YISHUN) +
  tm_polygons() +
tm_shape(lixel_hawker_new_YISHUN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_new_YISHUN)+
  tm_dots(col = "Point Type")
```

## Observation
:::

# Park

::: panel-tabset
## Import Park RDS

```{r}
#| eval: false
# set directory
setwd("data/rds/facilities/combined/park")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Import Lixel

```{r}
#| eval: false
# set directory
setwd("data/rds/lixel/park")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Ang Mo Kio

```{r}
#| eval: false
tm_shape(shape_ANG_MO_KIO) +
  tm_polygons() +
tm_shape(lixel_park_ANG_MO_KIO)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_ANG_MO_KIO)+
  tm_dots(col = "Point Type")
```

## Bedok

```{r}
#| eval: false
tm_shape(shape_BEDOK) +
  tm_polygons() +
tm_shape(lixel_park_BEDOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_BEDOK)+
  tm_dots(col = "Point Type")
```

## Bishan

```{r}
#| eval: false
tm_shape(shape_BISHAN) +
  tm_polygons() +
tm_shape(lixel_park_BISHAN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_BISHAN)+
  tm_dots(col = "Point Type")
```

## Bukit Batok

```{r}
#| eval: false
tm_shape(shape_BUKIT_BATOK) +
  tm_polygons() +
tm_shape(lixel_park_BUKIT_BATOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_BUKIT_BATOK)+
  tm_dots(col = "Point Type")
```

## Bukit Merah

```{r}
#| eval: false
tm_shape(shape_BUKIT_MERAH) +
  tm_polygons() +
tm_shape(lixel_park_BUKIT_MERAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_BUKIT_MERAH)+
  tm_dots(col = "Point Type")
```

## Bukit Panjang

```{r}
#| eval: false
tm_shape(shape_BUKIT_PANJANG) +
  tm_polygons() +
tm_shape(lixel_park_BUKIT_PANJANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_BUKIT_PANJANG)+
  tm_dots(col = "Point Type")
```

## Bukit Timah

```{r}
#| eval: false
tm_shape(shape_BUKIT_TIMAH) +
  tm_polygons() +
tm_shape(lixel_park_BUKIT_TIMAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_BUKIT_TIMAH)+
  tm_dots(col = "Point Type")
```

## Choa Chu Kang

```{r}
#| eval: false
tm_shape(shape_CHOA_CHU_KANG) +
  tm_polygons() +
tm_shape(lixel_park_CHOA_CHU_KANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_CHOA_CHU_KANG)+
  tm_dots(col = "Point Type")
```

## Clementi

```{r}
#| eval: false
tm_shape(shape_CLEMENTI) +
  tm_polygons() +
tm_shape(lixel_park_CLEMENTI)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_CLEMENTI)+
  tm_dots(col = "Point Type")
```

## Geylang

```{r}
#| eval: false
tm_shape(shape_GEYLANG) +
  tm_polygons() +
tm_shape(lixel_park_GEYLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_GEYLANG)+
  tm_dots(col = "Point Type")
```

## Hougang

```{r}
#| eval: false
tm_shape(shape_HOUGANG) +
  tm_polygons() +
tm_shape(lixel_park_HOUGANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_HOUGANG)+
  tm_dots(col = "Point Type")
```

## Jurong East

```{r}
#| eval: false
tm_shape(shape_JURONG_EAST) +
  tm_polygons() +
tm_shape(lixel_park_JURONG_EAST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_JURONG_EAST)+
  tm_dots(col = "Point Type")
```

## Jurong West

```{r}
#| eval: false
tm_shape(shape_JURONG_WEST) +
  tm_polygons() +
tm_shape(lixel_park_JURONG_WEST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_JURONG_WEST)+
  tm_dots(col = "Point Type")
```

## Kallang

```{r}
#| eval: false
tm_shape(shape_KALLANG) +
  tm_polygons() +
tm_shape(lixel_park_KALLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_KALLANG)+
  tm_dots(col = "Point Type")
```

## Marine Parade

```{r}
#| eval: false
tm_shape(shape_MARINE_PARADE) +
  tm_polygons() +
tm_shape(lixel_park_MARINE_PARADE)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_MARINE_PARADE)+
  tm_dots(col = "Point Type")
```

## Novena

```{r}
#| eval: false
tm_shape(shape_NOVENA) +
  tm_polygons() +
tm_shape(lixel_park_NOVENA)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_NOVENA)+
  tm_dots(col = "Point Type")
```

## Outram

```{r}
#| eval: false
tm_shape(shape_OUTRAM) +
  tm_polygons() +
tm_shape(lixel_park_OUTRAM)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_OUTRAM)+
  tm_dots(col = "Point Type")
```

## Pasir Ris

```{r}
#| eval: false
tm_shape(shape_PASIR_RIS) +
  tm_polygons() +
tm_shape(lixel_park_PASIR_RIS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_PASIR_RIS)+
  tm_dots(col = "Point Type")
```

## Punggol

```{r}
#| eval: false
tm_shape(shape_PUNGGOL) +
  tm_polygons() +
tm_shape(lixel_park_PUNGGOL)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_PUNGGOL)+
  tm_dots(col = "Point Type")
```

## Queenstown

```{r}
#| eval: false
tm_shape(shape_QUEENSTOWN) +
  tm_polygons() +
tm_shape(lixel_park_QUEENSTOWN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_QUEENSTOWN)+
  tm_dots(col = "Point Type")
```

## Rochor

```{r}
#| eval: false
tm_shape(shape_ROCHOR) +
  tm_polygons() +
tm_shape(lixel_park_ROCHOR)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_ROCHOR)+
  tm_dots(col = "Point Type")
```

## Sembawang

```{r}
#| eval: false
tm_shape(shape_SEMBAWANG) +
  tm_polygons() +
tm_shape(lixel_park_SEMBAWANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_SEMBAWANG)+
  tm_dots(col = "Point Type")
```

## Sengkang

```{r}
#| eval: false
tm_shape(shape_SENGKANG) +
  tm_polygons() +
tm_shape(lixel_park_SENGKANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_SENGKANG)+
  tm_dots(col = "Point Type")
```

## Serangoon

```{r}
#| eval: false
tm_shape(shape_SERANGOON) +
  tm_polygons() +
tm_shape(lixel_park_SERANGOON)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_SERANGOON)+
  tm_dots(col = "Point Type")
```

## Tampines

```{r}
#| eval: false
tm_shape(shape_TAMPINES) +
  tm_polygons() +
tm_shape(lixel_park_TAMPINES)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_TAMPINES)+
  tm_dots(col = "Point Type")
```

## Tanglin

```{r}
#| eval: false
tm_shape(shape_TANGLIN) +
  tm_polygons() +
tm_shape(lixel_park_TANGLIN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_TANGLIN)+
  tm_dots(col = "Point Type")
```

## Toa Payoh

```{r}
#| eval: false
tm_shape(shape_TOA_PAYOH) +
  tm_polygons() +
tm_shape(lixel_park_TOA_PAYOH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_TOA_PAYOH)+
  tm_dots(col = "Point Type")
```

## Tuas

```{r}
#| eval: false
tm_shape(shape_TUAS) +
  tm_polygons() +
tm_shape(lixel_park_TUAS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_TUAS)+
  tm_dots(col = "Point Type")
```

## Woodlands

```{r}
#| eval: false
tm_shape(shape_WOODLANDS) +
  tm_polygons() +
tm_shape(lixel_park_WOODLANDS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_WOODLANDS)+
  tm_dots(col = "Point Type")
```

## Yishun

```{r}
#| eval: false
tm_shape(shape_YISHUN) +
  tm_polygons() +
tm_shape(lixel_park_YISHUN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_park_YISHUN)+
  tm_dots(col = "Point Type")
```

## Observation
:::

# Healthy Hawkers

::: panel-tabset
## Import Healthy Hawkers RDS

```{r}
#| eval: false
# set directory
setwd("data/rds/facilities/combined/hawker_healthy")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Import Lixel

```{r}
#| eval: false
# set directory
setwd("data/rds/lixel/hawker_healthy")

# list all .rds files
files <- list.files(pattern = ".rds")

# loop through files and create separate dataframes
for (file in files) {
  # read in file and create dataframe with unique name
  df_name <- sub(".rds", "", file)
  assign(df_name, readRDS(file))
}
```

## Ang Mo Kio

```{r}
#| eval: false
tm_shape(shape_ANG_MO_KIO) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_ANG_MO_KIO)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_ANG_MO_KIO)+
  tm_dots(col = "Point Type")
```

## Bedok

```{r}
#| eval: false
tm_shape(shape_BEDOK) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_BEDOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_BEDOK)+
  tm_dots(col = "Point Type")
```

## Bishan

```{r}
#| eval: false
tm_shape(shape_BISHAN) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_BISHAN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_BISHAN)+
  tm_dots(col = "Point Type")
```

## Bukit Batok

```{r}
#| eval: false
tm_shape(shape_BUKIT_BATOK) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_BUKIT_BATOK)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_BUKIT_BATOK)+
  tm_dots(col = "Point Type")
```

## Bukit Merah

```{r}
#| eval: false
tm_shape(shape_BUKIT_MERAH) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_BUKIT_MERAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_BUKIT_MERAH)+
  tm_dots(col = "Point Type")
```

## Bukit Panjang

```{r}
#| eval: false
tm_shape(shape_BUKIT_PANJANG) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_BUKIT_PANJANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_BUKIT_PANJANG)+
  tm_dots(col = "Point Type")
```

## Bukit Timah

```{r}
#| eval: false
tm_shape(shape_BUKIT_TIMAH) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_BUKIT_TIMAH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_BUKIT_TIMAH)+
  tm_dots(col = "Point Type")
```

## Choa Chu Kang

```{r}
#| eval: false
tm_shape(shape_CHOA_CHU_KANG) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_CHOA_CHU_KANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_CHOA_CHU_KANG)+
  tm_dots(col = "Point Type")
```

## Clementi

```{r}
#| eval: false
tm_shape(shape_CLEMENTI) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_CLEMENTI)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_CLEMENTI)+
  tm_dots(col = "Point Type")
```

## Geylang

```{r}
#| eval: false
tm_shape(shape_GEYLANG) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_GEYLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_GEYLANG)+
  tm_dots(col = "Point Type")
```

## Hougang

```{r}
#| eval: false
tm_shape(shape_HOUGANG) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_HOUGANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_HOUGANG)+
  tm_dots(col = "Point Type")
```

## Jurong East

```{r}
#| eval: false
tm_shape(shape_JURONG_EAST) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_JURONG_EAST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_JURONG_EAST)+
  tm_dots(col = "Point Type")
```

## Jurong West

```{r}
#| eval: false
tm_shape(shape_JURONG_WEST) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_JURONG_WEST)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_JURONG_WEST)+
  tm_dots(col = "Point Type")
```

## Kallang

```{r}
#| eval: false
tm_shape(shape_KALLANG) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_KALLANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_KALLANG)+
  tm_dots(col = "Point Type")
```

## Marine Parade

```{r}
#| eval: false
tm_shape(shape_MARINE_PARADE) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_MARINE_PARADE)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_MARINE_PARADE)+
  tm_dots(col = "Point Type")
```

## Novena

```{r}
#| eval: false
tm_shape(shape_NOVENA) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_NOVENA)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_NOVENA)+
  tm_dots(col = "Point Type")
```

## Outram

```{r}
#| eval: false
tm_shape(shape_OUTRAM) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_OUTRAM)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_OUTRAM)+
  tm_dots(col = "Point Type")
```

## Pasir Ris

```{r}
#| eval: false
tm_shape(shape_PASIR_RIS) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_PASIR_RIS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_PASIR_RIS)+
  tm_dots(col = "Point Type")
```

## Punggol

```{r}
#| eval: false
tm_shape(shape_PUNGGOL) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_PUNGGOL)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_PUNGGOL)+
  tm_dots(col = "Point Type")
```

## Queenstown

```{r}
#| eval: false
tm_shape(shape_QUEENSTOWN) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_QUEENSTOWN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_QUEENSTOWN)+
  tm_dots(col = "Point Type")
```

## Rochor

```{r}
#| eval: false
tm_shape(shape_ROCHOR) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_ROCHOR)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_ROCHOR)+
  tm_dots(col = "Point Type")
```

## Sembawang

```{r}
#| eval: false
tm_shape(shape_SEMBAWANG) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_SEMBAWANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_SEMBAWANG)+
  tm_dots(col = "Point Type")
```

## Sengkang

```{r}
#| eval: false
tm_shape(shape_SENGKANG) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_SENGKANG)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_SENGKANG)+
  tm_dots(col = "Point Type")
```

## Serangoon

```{r}
#| eval: false
tm_shape(shape_SERANGOON) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_SERANGOON)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_SERANGOON)+
  tm_dots(col = "Point Type")
```

## Tampines

```{r}
#| eval: false
tm_shape(shape_TAMPINES) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_TAMPINES)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_TAMPINES)+
  tm_dots(col = "Point Type")
```

## Tanglin

```{r}
#| eval: false
tm_shape(shape_TANGLIN) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_TANGLIN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_TANGLIN)+
  tm_dots(col = "Point Type")
```

## Toa Payoh

```{r}
#| eval: false
tm_shape(shape_TOA_PAYOH) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_TOA_PAYOH)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_TOA_PAYOH)+
  tm_dots(col = "Point Type")
```

## Tuas

```{r}
#| eval: false
tm_shape(shape_TUAS) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_TUAS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_TUAS)+
  tm_dots(col = "Point Type")
```

## Woodlands

```{r}
#| eval: false
tm_shape(shape_WOODLANDS) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_WOODLANDS)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_WOODLANDS)+
  tm_dots(col = "Point Type")
```

## Yishun

```{r}
#| eval: false
tm_shape(shape_YISHUN) +
  tm_polygons() +
tm_shape(lixel_hawker_healthy_YISHUN)+
  tm_lines(col="density", lwd=2)+
tm_shape(hdb_hawker_healthy_YISHUN)+
  tm_dots(col = "Point Type")
```

## Observation
:::
